Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-05-03 doc/RMD/mlg-mcg.Rmd
add severity graph

>>>>

There are a whole buttload of MLGs for those 5 MCGs. What are the severity 
ratings for those?

```{r severity, fig.width = 7, fig.height = 7}

strat <- bind_cols(strata(dat11), 
                   other(dat11)$meta, 
                   data_frame(MLG = mll(dat11, "original")))
Severity <- filter(strat, MCG %in% mcgs$MCG[1:5])
ggplot(Severity, aes(x = MCG, y = Severity)) +
  geom_point(aes(fill = ifelse(MLG %in% mlgs$MLG[1:5], MLG, "Other")), 
             position = position_jitter(width = 0.25),
             alpha = 0.75,
             pch = 21) +
  scale_fill_viridis(discrete = TRUE, direction = -1) +
  facet_wrap(~Region, ncol = 2) +
  labs(list(
    title = "Severity by MCG and Region",
    fill = "Multilocus Genotype",
    caption = "Five most abundant multilocus genotypes shown"
  ))
```
